### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9a12647fe4aedea387c0b211284a79dddb676f28 🚀

>>>>

These two analyses point to the following recommendations: MCC is indeed
more appropriate than \(\kappa\), as although sensitive to bias, it is
sensitive in a consistent way. Informedness is appropriate at
discriminating between different skills, but confounded by bias. \(F_1\)
is increasing with bias, and should not be prioritized to evalue the
performance of the model. The discussion of sensitivity to bias should
come with a domain-specific caveat: although it is likely that
interactions documented in ecological networks are correct, a lot of
non-interactions are simply unobserved; as predictive models are used
for data-inflation (\emph{i.e.} the prediction of new interactions), it
is not necessarilly a bad thing to select models that predict more
interactions than the original dataset, because the original dataset
misses some interactions.
